---
title: "ETC5512 Assignment 3: State of the Gender Gap"
author:
- familyname: Mysore Venkatesh
  othernames: Rahul Bharadwaj
  title: Mr
  qualifications: Master of Business Analytics
  email: rmys0001@student.monash.edu
  correspondingauthor: true
department: Department of\newline Econometrics &\newline Business Statistics
organization: Monash University
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  MonashEBSTemplates::report:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r libraries, message = FALSE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(kableExtra)
library(bookdown)
library(treemap)
library(knitr)
library(viridis)
library(scales)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, message=FALSE, warning = FALSE)
```

# Will's section.

```{r Loading dataset,echo = FALSE}
dat <- read.csv(here::here("Data/IMDb movies.csv"))
glimpse(dat)
```

```{r metascoretable}
dat %>% 
        dplyr::select(metascore) %>%
        summary() %>%
        kable(caption = "Metascore summary") %>%
        kable_styling(bootstrap_options = c("striped", "hover"))
```


According to IMDb, metascore is a single number that represents the overall critical opinion about a movie. Its legitimacy is derived from applying a weighted average to the reviews of the world's most respected critics. That said, metascore is still an extremely vague concept - particularly when it comes to the threshold of what metascore can be considered good.

Therefore, it is important to first consider the distribution of metascore within the data set. This is summarised by Table \@ref(tab:metascoretable). The most noteworthy features are that the median and mean are very close at 56 and 55.76 respectively and nearly 70,000 movies have not been assigned a metascore. Consequently, any analysis related to the metascore variable must be treated with caution as less than 20% of the movies are represented. 

```{r metascorescatterplot, warning = FALSE, fig.cap = "metascore vs time"}
f1wn = dat %>%
             ggplot(aes(x = year, y = metascore)) + 
             geom_point()
f1wn
```

As expected, the scatter plot depicted in Figure \@ref(fig:metascorescatterplot) is not particularly informative and potentially misleading. Although the spread is increasing, one can still identify a negative correlation which suggests that the quality of movies has degraded over time. However, it is important to recognise that this dataset was taken from IMDb which means that sampling was far from random. IMDb has much more incentive to review recently released movies. Hence, when older movies are reviewed, it is likely because it is still immensely popular (i.e. a 'classic').

```{r toptwentytable}
dat2wn <- dat %>%
               dplyr::select(title,
                             year,
                             metascore)

dat3wn <- dat2wn %>%
                arrange(-metascore)

dat3wn %>%
        head(20) %>%
        kable(caption = "The top 20 movies arranged by metascore") %>%
        kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r toptwentyhistogram, fig.cap = "Time distribution of top twenty movies"}
dat3wn %>%
        head(20) %>%
        ggplot(aes(year)) + 
        geom_histogram(binwidth = 5) +
        xlab("Year") +
        ylab("")
```

The aforementioned 'classics bias' is further confirmed by both Table \@ref(tab:toptwentytable) and Figure \@ref(fig:toptwentyhistogram). This list is dominated by the most famous movies from the 1900's such as The Wizard of Oz, Citizen Kane and The Godfather which were all assigned perfect metascores. Moreover, seventeen of the twenty listed movies were released before 1975 and only one was released after 2000.

Assuming that metascore is a reliable representation of a movie's quality, it is easy to see why arguments have been made that movies produced in recent times are not as good. Contrarily, a counterargument can be made that there were just as many bad movies made during previous generations that have been forgotten or overshadowed by the classics. Due to the clear bias within this dataset, it is still unclear which argument is stronger. 

\newpage
# Xue Wang section

## Language
 
### The proportion of top 100 movie language

```{r language, echo=FALSE, fig.cap = "The proportion of top 100 movie language", warning=FALSE, fig.height=6, fig.pos="H"}
top100 <- head(names(sort(table(dat$language),decreasing = TRUE)),100) 
most_language <- dat %>% 
    filter(language %in% top100) %>% 
    group_by(language) %>%
    summarize(total = n()) %>%
    arrange(-total) %>%
    treemap(publisher_tm, index = "language",
            vSize = "total",
            fontsize.labels = 12,
            palette = "YlOrRd",
            title = "The proportion of top 100 movie language", fontsize.title = 20)
```

The figure \@ref(fig:language) shows the proportion of the number top 100 languages. It can clearly be seen that the English movies account for almost half of all movies. French, Spanish, Japanese, Italian almost have the same proportion with the number of above 2500. It is very clear to see the situation about the distribution. 

### Number of top 9 languages between 2009 and 2019

```{r langyear, echo = FALSE, fig.cap = "Top 9 languages between 2009 and 2019", warning=FALSE, fig.height=6, fig.pos="H"}

top9 <- dat %>% 
  filter(year %in% c(2009:2019)) 
top_9_last <- head(names(sort(table(top9$language),decreasing = TRUE)),9) 


language_9 <- dat %>% 
  select (year,language) %>% 
  filter(language %in% top_9_last ,year %in% c(2009:2019)) %>% 
  group_by (year,language) %>%  
  count(language)

language_9 %>% 
  ggplot(aes(x= year, y= n))+
  geom_line(color = "steelblue",size = 2)+
  facet_wrap(~ language,scales = "free_y")+
  scale_x_continuous(breaks = seq(2009, 2019, by = 1))+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=1)) +
  xlab("year")+
  ylab("Number of top 9 languages between 2009 and 2019")
```

The figure \@ref(fig:langyear) shows the number of different languages movies between 2009 and 2019. It can be clearly seen that the largest number of movie languages is English, it has an increasing trend between 2009 and 2017 and will drop to 600 in 2019. The number of  Korean language movies have the minimum quantity within the 9 languages, it shows a decreasing trend during the ten years. The number of French,German, Japanese and Italian, they almost maintained the level from 2009 to 2017, and then sharply decreased to 2019.

## Genres 

The proportion of top 100 movie genres

```{r genres, echo = FALSE, fig.cap = "The proportion of top 100 movie genres", fig.height=6, fig.pos="H"}
top100_genre<- head(names(sort(table(dat$genre),decreasing = TRUE)),100) 
most_genre <- dat %>% 
    filter(genre %in% top100_genre) %>% 
    group_by(genre) %>%
    summarize(total = n()) %>%
    arrange(-total) %>%
    treemap(publisher_tm, index = "genre",
                  vSize = "total",
                  fontsize.labels = 12,
                  palette = "YlOrRd",
                  title="The proportion of top 100 movie genres",
     
                       fontsize.title = 20)
```

The figure \@ref(fig:genres) shows the  proportion of top 100 movie genres, from the figure, we can see that the drama and comedy almost occupied 30% of total movies, followed by the horror, comedy and romance, drama and romance, thriller.etc almost have the same proportion, this picture clearly shows the proportion of different movie genres.

### Number of top 10 genres of movies published from 2009 to 2019

```{r genresyear, echo = FALSE, fig.cap = "Number of top 10 types of movies published from 2009 to 2019", fig.height= 5, fig.pos="H"}
top10_genres <- dat %>% 
  filter(year %in% c(2009:2019)) 
top_10_genres <- head(names(sort(table(top10_genres$genre),decreasing = TRUE)),10) 

dat_genre <- dat %>% 
  select (genre,year) %>% 
  filter(genre %in%top_10_genres,year %in% c(2009:2019)) %>%
  group_by(genre,year) %>% 
  count(year) %>% 
  arrange(desc(n)) 

ggplot(dat_genre, aes(x = year, y = n))+
  geom_col()+
  geom_line(color = "red")+
  facet_wrap(~genre,scales = "free_y")+
  xlab ("Year") +
  ylab ("Number of movies") +
  ggtitle("Number of top 10 types of movies published from 2009 to 2019")+
  scale_x_continuous(breaks = seq(2009,2019, by = 1))+
  theme(axis.text.x = element_text(angle=90, hjust=1, vjust=1)) 
```

The figure \@ref(fig:genresyear) graph shows the change in the number of different movie genres in ten years, from this figure, it can be seen that,the number of dramas and comedies almost exceeds 100 every year, and dramas almost reach 500 every year. When it comes to the line chart, the number of almost all movie genres peaked in 2017 and then fell to 2019. This is because the  movie industry returns to the content ontology and enters the transition period from quantity to quality.

### The largest number of movies genres in each country

```{r maxgenres, echo = FALSE, fig.height=6, fig.pos="H"}
dat_genre_country <- dat %>% 
  select (country, genre,year) %>%  
  filter(year %in% c(2000:2020)) %>% 
  group_by(country) %>% 
  count(genre) 


max_dat_genre_country <- dat_genre_country %>%  
    group_by(country) %>% 
    filter( n==max(n)) %>% 
    arrange(desc(n)) 
kable(
max_dat_genre_country[1:10,],booktabs = TRUE, caption = ' The largest number of movies genres in each country' )
    

```

Table \@ref(tab:maxgenres) show the largest number of movies genres in each country in the 21st century, according to this table, we can see the the largest number of movies in many countries is drama, According Table \@ref(tab:pretdrame) , it shows the drama has the largest proportion with 58.84%, However, the second place comedy only reached 8%.

```{r pretdrame, echo = FALSE, fig.height=6, fig.pos="H"}

  drama_genre_country <- max_dat_genre_country%>% 
  group_by(genre) %>%  
  summarise(total = sum(n)) %>% 
  ungroup() %>% 
  mutate(total_movies = sum(total)) %>% 
  mutate(prop_genre= total / total_movies) %>% 
  arrange(desc(prop_genre)) %>% 
  head(5)

kable(
drama_genre_country[1:5,],booktabs = TRUE, caption = ' The largest number of movies genres in each country' )
```

\newpage
# Rahul's Section.

## Movie Grosses and Popularity Analysis

- What is the Budget and USA Gross for Avenger and Spider-Man movie franchises?

- What is the Number of user reviews and critic reviews for the same, implying their popularity?

- What is the gross of the most popular movies of all-time?

```{r LoadingDataset, message=FALSE, warning=FALSE, echo=FALSE}
#reading data from the csv file in "Data" folder
data <- read.csv(here::here("Data/IMDb movies.csv"))
#sample of raw data with columns and observations 
glimpse(data)
```

- The above chunk shows the column names of the raw dataset. The columns are selected based on the research questions to be answered. The column names are cleaned by renaming the columns clearly and prepared to be useful for analysis.

```{r CleaningData, echo=FALSE, message=FALSE, warning=FALSE}
#cleaning column names
cleandata <- data %>% rename(Title = title, Year = year, Language = language, Production_Company = production_company, Budget = budget, USA_Gross = usa_gross_income, User_Reviews = reviews_from_users, Critic_Reviews = reviews_from_critics) %>% select(Title, Year, Language, Production_Company, Budget, USA_Gross, User_Reviews, Critic_Reviews)
```

```{r PrepData, message=FALSE, warning=FALSE, echo=FALSE}
#tidying data by filtering null values
grossdata <- cleandata %>%  filter((!Budget == "" | NA), (!USA_Gross == "" | NA))
reviewdata <- cleandata %>%  filter((!User_Reviews == "" | NA), (!Critic_Reviews == "" | NA))
```

Tidyverse (@tidyverse) is used to clean the data and kableExtra (@kableExtra) is used to display tables.

```{r GrossTable, fig.pos="H", message=FALSE, warning=FALSE, echo=FALSE}
head(grossdata, 10) %>% select(Title, Budget, USA_Gross) %>% kable("latex", booktabs = T, caption = "Sample Gross Data Table") %>% 
  kable_styling( position = c("center", "hold"))
```

The table \@ref(tab:GrossTable) shows a sample of the gross data used for the analysis. The main columns needed for Gross analysis are Title, Budget, and USA_Gross.

```{r ReviewTable,  fig.pos="H", message=FALSE, warning=FALSE, echo=FALSE}
head(reviewdata, 10) %>% select(Title, User_Reviews, Critic_Reviews) %>% kable("latex", booktabs = T, caption = "Sample Review Data Table") %>% 
  kable_styling( position = c("center", "hold"))
```

The table \@ref(tab:ReviewTable) shows a sample of the review data used for the analysis. The main columns needed for Gross analysis are Title, User_Reviews, and Critic_Reviews.

Using the table contents, we plot data for a particular movie franchise. The franchises selected for this anlysis are Avengers and Spider-Man. We display plots to analyse how much the franchise spent for the movie and how much it grossed. Also a plot for the user reviews and critic reviews are displayed to see which were the most popular among all the movies in the franchise. We also plot the same for all the movies in the dataset.

```{r AvengersGross,fig.pos="H", fig.cap="Avengers Budget v/s Gross", fig.align="center", echo=FALSE, fig.height= 3}
#plotting budget vs gross for "Avengers Franchise"
grossdata %>% select(Title, Production_Company, Budget, USA_Gross) %>% 
  filter(Title %in% c("The Avengers", "Avengers: Age of Ultron", "Avengers: Infinity War", "Avengers: Endgame"), Production_Company == "Marvel Studios") %>% 
  ggplot(aes(x = Budget, y = USA_Gross, label = Title)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.25)+
  ggtitle("Avenger Movies Gross") + theme_bw()
```

From the figure \@ref(fig:AvengersGross), it can be seen that all Avenger movies grossed more than the amount spent. Avengers: Age of Ultron grossed relatively lesser than the other movies. Endgame was the highest grossing Avenger movie.


```{r AvengersReview,fig.pos="H", fig.cap="Avengers Popularity", fig.align="center", echo=FALSE, fig.height= 3}
#plotting number of user reviews and critic reviews for "Avengers Franchise"
reviewdata %>% select(Title, Year, Production_Company, User_Reviews, Critic_Reviews) %>% 
  filter(Title %in% c("The Avengers", "Avengers: Age of Ultron", "Avengers: Infinity War", "Avengers: Endgame"), Production_Company == "Marvel Studios") %>% 
  ggplot(aes(x = Critic_Reviews, y = User_Reviews, color = Title, label = Year)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.25)+
  ggtitle("Avenger Movies Popularity") + theme_bw()
```

The figure \@ref(fig:AvengersReview) displays how many reviews was given by users and critics. This can be a measure of how much the movies were talked about. The year tags show the timeline. It is evident that the first avenger movie in 2012 attracted the attention of critics with a high number of critic reviews. As time passed by, the movies become more popular among users which shows an increse in the fanbase till 2019. The only exception to this is a dip in user reviews for Age of Ultron which justifies why it grossed lesser than other movies.

```{r SpiderManPlot, fig.pos="H", fig.cap="Spider-Man Budget v/s Gross", fig.align="center", echo=FALSE, fig.height= 3}
#plotting budget vs gross for "Spider-Man Movies" 
grossdata %>% select(Title, Language, Production_Company, Budget, USA_Gross) %>% 
  filter(Title %in% c("Spider-Man", "Spider-Man 2", "Spider-Man 3", "The Amazing Spider-Man", "The Amazing Spider-Man 2", "Spider-Man: Homecoming", "Spider-Man: Far from Home")) %>%
  ggplot(aes(x = Budget, y = USA_Gross, label = Title)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.25)+
  ggtitle("Spider-Man Movies Gross") + theme_bw()
```

The figure \@ref(fig:SpiderManPlot) shows the budget and gross of Spider-Man movies. Spider-Man grossed the highest and the sequels Spider-Man 2 and Spider-Man 3 grossed lesser showing a decline in the gross. The Amazing Spider-Man seems to have grossed better than its sequel The Amazing Spider-Man 2. These movies has grossed far less than the first 3 movies. The Homecoming and Far from Home movies seem to have made a great comeback in terms of its gross compared to the fourth and fifth movies. Far from Home has grossed more and spent less which makes it the second best Spider-Man movie after the first ever one in the franchise.

The figure \@ref(fig:SpiderManReview) shows a graph for the number of reviews by critics and users over a period of time named by the years for each points. The first ever movie was most talked about by both fans and users in 2002. We see a dip in user reviews for 2004 and the movie in 2007 was a little better but the first ever was the best recieved. The fourth and fifth movies in 2012 and 2014 was talked about most by critics but never really kicked off among fans. This justifies its low grosses. The final sixth and seventh movies in 2017 and 2019 have made a great comeback after this dip and the latest one during 2019 has managed to almost equal the fanbase like it was when the franchise started.

```{r SpiderManReview, fig.pos="H", fig.cap="Spider-Man Popularity", fig.align="center", echo=FALSE, fig.height= 3}
#plotting number of user reviews and critic reviews for "Spider-Man Movies"
reviewdata %>% select(Title, Year, Production_Company, User_Reviews, Critic_Reviews) %>% 
  filter(Title %in% c("Spider-Man", "Spider-Man 2", "Spider-Man 3", "The Amazing Spider-Man", "The Amazing Spider-Man 2", "Spider-Man: Homecoming", "Spider-Man: Far from Home")) %>% 
  ggplot(aes(x = Critic_Reviews, y = User_Reviews, color = Title, label = Year)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.25)+
  ggtitle("Spider-Man Movies Popularity") + theme_bw()
```

```{r AllReviewsPlot, fig.pos="H", fig.cap="All-time Popularity", fig.align="center", echo=FALSE, warning=FALSE, fig.height= 5}
#plotting all-time user reviews and critic reviews for entire dataset
reviewdata %>%
  ggplot(aes(x = Critic_Reviews, y = User_Reviews, label = Title)) +
  geom_point() +
  geom_text(vjust = "inward", hjust = "inward") +
  xlim(0, 1000) +
  ggtitle("Most-Talked-About Movies by Users & Critics") + theme_bw()
```

The figure \@ref(fig:AllReviewsPlot) looks shabby when you first look at it but it has some insights that can be drawn from it. The black cluster at the left bottom are the movies that have a low number of reviews by both users and critics. These are the least popular movies. The outliers are clearly visible in this plot with Endgame being the most popular among fans around the globe. This plot is used to pick the most popular movies to be used to compare the budget and gross. It is not necessary for a movie to be good, to be most talked about. So the next plot serves as a verification to confirm if the movie was talked about because it was good, or bad.

```{r AllGrossPlot, fig.pos="H", fig.cap="Some all-time Popular Movies and their Gross", fig.align="center", echo=FALSE, warning=FALSE, fig.height= 5}
#plotting all-time budget vs gross for some of the most reviewed movies
grossdata %>% select(Title, Year, Budget, USA_Gross) %>% 
  filter(Title %in% c("Avengers: Endgame", "Joker", "The Shawshank Redemption", "Captain Marvel", "The Dark Knight", "Star Wars: Episode VIII - The Last Jedi", "The Lord of the Rings: The Fellowship of the Ring", "Avengers: Infinity War", "The Matrix", "Avatar", "Star Wars: Episode VII - The Force Awakens", "Once Upon a Time in Hollywood", "Black Panther", "The Godfather", "The Godfather: Part II", "The Godfather: Part III", "Bohemian Rhapsody", "Man of Steel", "Prometheus", "Batman v Superman: Dawn of Justice", "Star Wars: Episode I - The Phantom Menace", "Indiana Jones and the Kingdom of the Crystal Skull", "The Shape of Water")) %>%
  ggplot(aes(x = Budget, y = USA_Gross, label = Title, color = Year)) +
  geom_point() +
  geom_text(vjust = "inward", hjust = "inward")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("'Most-talked-about' Movies & their Gross") +
  scale_color_viridis(begin = 1, end = 0)
```

The figure \@ref(fig:AllGrossPlot) shows the budget and gross of the most popular movies from over a century. We can compare the production cost, which is the budget, and the gross to ensure that it was most talked about because it was good. This plot also has information about the decade it was released in. This was to ensure there was no bias between the movies since currency value is always changing. The values are discrete and shows how much was spent and how much was grossed for that time. The gradient is gven to year using Viridis.

## Conclusion

In conclusion, we can see a general trend that a movie that is most talked about by the users or fans has grossed the most amount of money compared to lesser popular movies. The number of reviews by users can generally be used to predict if it was a box office hit.

\newpage
# Aryan's Section.

## Director Analysis

### Most Successful Director

Lets take a look at the some of the most successful directors from our dataset. Now, there are limitless ways to measure success but for our test, we're only looking at people with at least 4 movies under their belt and a Metascore upwards of 80. And conveniently, we get only 10 names.

```{r 1}
directors <- dat %>%
  group_by(director) %>%
  summarise(movies = n(),
            metascore = round(mean(metascore))) %>%
  filter(metascore > 80,
         movies > 3) %>%
  arrange(-metascore, -movies)
```

```{r dir_tab, fig.cap="Top Grossing Movies"}
directors %>%
kable(col.names = c("Director",
                      "Total Movies",
                      "Metascore")) %>%
  kable_styling()
```

We get some interesting results, as on one hand there is Mike Leigh with as much as 13 movies but a lower average metascore. On the other hand, there are directors like Damien Chazelle and Patrick wang with 4 movies each and an average metascore of 87 and 86 respectively. 

```{r 2}
directors %>%
  ggplot(aes(x = director, y = movies, fill = metascore)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  xlab("") +
  ylab("No. of Movies")
```

## Top Grossing Movie

In this section, we'll look at the top grossing movie of the most successful directors that we established from Table \@ref(tab:dir_tab).

```{r 3}
director_movie <- dat %>%
  right_join(directors, by = c("director" = "director")) %>%
  select(director, title, worlwide_gross_income)

director_movie$worlwide_gross_income = as.numeric(gsub("[\\$,]", "", director_movie$worlwide_gross_income))

director_movie_final <- director_movie %>% 
  group_by(director) %>%
  summarise(worlwide_gross_income = max(worlwide_gross_income, na.rm = TRUE)) %>%
  left_join(director_movie)

director_movie_final %>%
  select(director, title, worlwide_gross_income) %>%
  arrange(-worlwide_gross_income) %>%
  mutate(worlwide_gross_income = dollar(worlwide_gross_income)) %>%
  kable(col.names = c("Director",
                      "Highest Grossing Movie",
                      "Total Revenue")) %>%
  kable_styling()
```

It can be observed that the *Alfonso Cuarón* is the director of the top grossing movie *Harry Potter and the Prisoner of Azkaban* which made \$796,093,802 worldwide. Followed by, *Damien Chazelle*, the director of *La La Land* grossing \$446,092,35. Suprisingly, *Patrick Wang*, with an average metascore of 86 and a total of 4 movies made the least at just \$101,934.

```{r 4, fig.align="center", fig.cap="Top Grossing Movies"}
director_movie_final %>%
  mutate(director = fct_reorder(director, worlwide_gross_income)) %>%
  ggplot(aes(y = worlwide_gross_income, x = director, fill = title)) +
  geom_col() +
  theme(legend.position = "right", legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(label = comma) +
  xlab("") +
  ylab("")
```

## Movie Length and Language Analysis

```{r 5}
dat1 <- dat
dat1$language <- ifelse(str_detect(dat1$language, ","), "multi-lingual", dat1$language)
dat1$budget = as.numeric(gsub("[\\$,]", "", dat1$budget))
```

### Let's look at some of the common movie languages.

```{r 6}
dat2 <- dat1 %>%
  count(language) %>%
  arrange(-n) %>%
  head(10)
```

```{r 7}
dat2 %>%
  kable(col.names = c("Language", "Number of Movies")) %>%
  kable_styling()
```

From the above table, it is quite clear that most movies are released in either only *English* or in *multi-lingual* format.

```{r 8}
dat3 <- dat1 %>%
  filter(language %in% dat2$language) %>%
  group_by(language) %>%
  summarise(duration = mean(duration, na.rm = TRUE))
```

### Is there a pattern in Movie length for various languages?

```{r 9}
dat3 %>%
  kable(col.names = c("Language", "Avg. Movie Duration")) %>%
  kable_styling()
```

```{r 10, fig.align="center"}
dat3 %>%
  ggplot(aes(x = language, y = duration, fill = language)) +
  geom_col() +
  ylab("Duration (in minutes)") +
  xlab("") + 
  theme(legend.position = "bottom", axis.text.x=element_blank())
```

From the plot above, we can infer that *Hindi* movies are usually much longer than other languages clocking at an average runtime of 140 minutes. While, *English* movies are usually the shortest at just 93 minutes.

## Conclusion

There appears to be a strong correlation between movies that have been given extremely high ratings and the mid 1950's. However, due to the inherent bias within this data set, it is still impossible to identify which periods truly experienced a higher quality of movie production.

For Director analysis, it is clear from Figure 1 and Figure 2 that there is no one single way to measure success and that all directors in the list are doing very good in their own ways.

And from the Movie length analysis, we can infer that Hindi Movies are usually significantly longer than any other kind of movies. Also, english movies are among the shortest. We also concluded that movie language has an impact on movie length.

# Citations

tidyverse @tidyverse

dplyr @dplyr

kableExtra @kableExtra

bookdown @bookdown

treemap @treemap

scales @scales

viridis @viridis