---
title: "5513 - Assignment 4"
author: "Aryan Jain"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE)
```

```{r Loading dataset}
dat = read.csv("Data/IMDb movies.csv")
```

```{r}
library(tidyverse)
library(scales)
library(kableExtra)
```

## Director Analysis

#### Most Successful Director

Lets take a look at the some of most successful directors from our dataset. Now, there are limitless ways to measure success but for our test, we're only looking at people with at least 4 movies under their belt and a Metascore upwards of 80. And conveniently, we get only 10 names.

```{r}
directors <- dat %>%
  group_by(director) %>%
  summarise(movies = n(),
            metascore = round(mean(metascore))) %>%
  filter(metascore > 80,
         movies > 3) %>%
  arrange(-metascore, -movies)
```

```{r dir_tab}
directors %>%
kable(col.names = c("Director",
                      "Total Movies",
                      "Metascore"),
      caption = "Successful Directors") %>%
  kable_styling()
```

We get some interesting results, as on one hand there is Mike Leigh with as much as 13 movies but a lower average metascore. On the other hand, there are directors like Damien Chazelle and Patrick wang with 4 movies each and an average metascore of 87 and 86 respectively. 